Spfy: bringing real-time, big data batch analyses of E. coli to SuperPhy

### 2017-12-22 paper-proposal.tex
EDIT: affil
EDIT: authors, email

\author{%
Kevin K Le\,$^{1, *}$,
Matthew D Whiteside\,$^{1}$,
Chad R Laing\,$^{1}$,
and Victor PJ Gannon\,$^{1}$
\footnote{To whom correspondence should be addressed.
Tel: +1 403-382-5516; Fax: +1 403-381-1202; Email: chad.r.laing@phac-aspc.gc.ca}}

\address{%
$^{1}$Laboratory for Foodborne Zoonoses, Public Health Agency of Canada, Twp Rd 9-1, Lethbridge, AB, T1J 3Z4, Canada}
% Affiliation must include:
% Department name, institution name, full road and district address,
% state, Zip or postal code, country

>>>>

\author{%
Kevin K Le\,$^{1, *}$,
Matthew D Whiteside\,$^{1}$,
James Hopkins\,$^{1}$,
Victor PJ Gannon\,$^{1}$,
and Chad R Laing\,$^{1}$}
\footnote{To whom correspondence should be addressed.
Tel: +1 403-382-5516; Fax: +1 403-381-1202; Email: chad.laing@canada.ca}

\address{%
$^{1}$National Microbiology Laboratory at Lethbridge, Public Health Agency of Canada, Twp Rd 9-1, Lethbridge, AB, T1J 3Z4, Canada}
% Affiliation must include:
% Department name, institution name, full road and district address,
% state, Zip or postal code, country

### 2017-12-22 paper-proposal_raw.tex
EDIT: affil
EDIT: authors, email

Kevin K Le\,$^{1}$,
Matthew D Whiteside\,$^{1}$,
Chad R Laing\,$^{1}$,
and Victor PJ Gannon\,$^{1}$

$^{1}$Laboratory for Foodborne Zoonoses, Public Health Agency of Canada, Twp Rd 9-1, Lethbridge, AB, T1J 3Z4, Canada

Tel: +1 403-382-5516; Fax: +1 403-381-1202; Email: chad.r.laing@phac-aspc.gc.ca

>>>>

Kevin K Le\,$^{1, *}$,
Matthew D Whiteside\,$^{1}$,
James Hopkins\,$^{1}$,
Victor PJ Gannon\,$^{1}$,
and Chad R Laing\,$^{1}$

$^{1}$National Microbiology Laboratory at Lethbridge, Public Health Agency of Canada, Twp Rd 9-1, Lethbridge, AB, T1J 3Z4, Canada

Tel: +1 403-382-5516; Fax: +1 403-381-1202; Email: chad.laing@canada.ca
